### 2022-07-30 paper/akweury/document.tex
update nnnn model

\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train. It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map. For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of Trip-Net architecture. Since the Trip-Net is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the simplification. A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times. We evaluate the fusion times from 1 to 4. Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.

@@

\begin{figure}[th]
	\centering
	\includegraphics[width=.8\textwidth]{./Figures/gcnn_loss_compare.png}
	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
	\label{fig:trip-net-training-history}
\end{figure}

>>>>

\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train. It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map. For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of Trip-Net architecture. Since the Trip-Net is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification. A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $, where $ x $ denotes the fusion times. We evaluate the fusion times from 1 to 4. Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss.

@@

\begin{figure}[th]
	\centering
	\includegraphics[width=.8\textwidth]{./Figures/trip_net_loss.png}
	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
	\label{fig:trip-net-training-history}
\end{figure}
